Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-10-11 paper/paper_draft.qmd
Ensure correct julia version is used by Quarto

keywords:
  - Coral reef
  - Climate change
  - Ecosystem resilience
  - Reef depth
  - Reef connectivity
date: last-modified
format:
  elsevier-docx:
    journal:
      name: Journal Name
      formatting: preprint
      cite-style: authoryear
bibliography: references.bib
engine: julia
crossref:
  custom:
  - kind: float
    reference-prefix: SFigure
    key: sfig
  - kind: float
    reference-prefix: STable
    key: stbl
editor:
  markdown:
    wrap: 92
    canonical: true
---

>>>>

keywords:
  - Coral reef
  - Climate change
  - Ecosystem resilience
  - Reef depth
  - Reef connectivity
date: last-modified
format:
  elsevier-docx:
    journal:
      name: Journal Name
      formatting: preprint
      cite-style: authoryear
bibliography: references.bib
engine: julia
julia:
  exeflags: ["+1.11.5"]
crossref:
  custom:
  - kind: float
    reference-prefix: SFigure
    key: sfig
  - kind: float
    reference-prefix: STable
    key: stbl
editor:
  markdown:
    wrap: 92
    canonical: true
---
